### 2016-01-05 doc/tutorial/detailed.Rmd
add some more unit tests

>>>>

## Calling findSoftware (or other methods) result in 'no applicable method for 'findSoftware' applied to an object of class...'

This means that the wrapper for your SVM was not found, therefore no object was created, and the findSoftware could not be executed, because it is simply not there. Double check that adding the SVM package works for you, e.g. by enabling verbose mode.
'
